### 2018-10-25 inst/table_tennis_serve.Rmd
Change the order of the players from a,b,c,S to S,a,b,c.
The previous ordering, a,b,c,S, was unnecessarily difficult because
the additional constraint (additional in the sense of additional over
and above "0 <= p_A, p_B, p_C, p_S<1" and "p_A + p_B + p_C <= 1") was
on the fillup value p_S, so "p_S<=small" was forced to appear as
"p_A+p_B+p_C>=1-small", which was confusing as the constraint on p_S
was written in terms of the other strengths.

Now we have S,a,b,c this is easier.  We have the additional constraint
appearing as the much simpler form "p_S<small".

Actually, now that I write it like

```{r}
H <- hyper2(pnames=c("a","b","c","S"))
```

@@

```{r}
small <- 1e-6
maxlike_constrained <-
    constrOptim(
        f = function(p){loglik(H,p)},
        theta=rep(1/3,3)-small,
        grad=NULL,
        ui=rbind(diag(3),-diag(3),1,-1),
        ci=c(rep(small,3),rep(small,3)-1, 1-4*small, small*2-1),
        control=list(fnscale = -1)  # finds max, not min
    )
```

>>>>

```{r}
H <- hyper2(pnames=c("S","a","b","c"))
```

@@

```{r}
small <- 1e-6
maxlike_constrained <-
    constrOptim(
        f = function(p){loglik(H,p)},
        theta=c(small, 1/3-small/2, 1/3-small/2),
        grad=NULL,
        ui=rbind(diag(3),-diag(3),-1),
        ci=c(rep(small/2,3),c(-small*2,-1,-1),-1),
        control=list(fnscale = -1)  # finds max, not min
    )
```
